---
title: "plots-ggplot.Rmd"
author: "Ankit Sharma"
date: "20/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(readxl)
library(here)
ca_np <- read_csv(here("data", "ca_np.csv"))
names(ca_np)
head(ca_np)
summary(ca_np)
```

ci_np <- read_excel(here("data", "ci_np.xlsx"))
view(ci_np)
names(ci_np)
head(ci_np)
summary(ci_np)

ggplot(data = df_name, aes(x = x_var_name, y = y_var_name)) +
  geom_type()
ggplot(data = ci_np, aes(x = year, y = visitors)) +
  geom_line()
gg_base <- ggplot(data = ci_np, aes(x = year, y = visitors))
gg_base + geom_point()
gg_base + geom_col()
gg_base + geom_area()

gg_base + geom_line(color="purple", linetype= "dashed")
gg_base + geom_point(color = "purple", pch = 4, size=4, alpha=0.5)
gg_base + geom_point(aes(size = visitors, color = visitors), alpha=0.5)

gg_base + geom_col(aes(fill = visitors))
gg_base + geom_point(aes(size = visitors, color = visitors), alpha=0.5) + theme_minimal()

gg_base + geom_line(linetype = "dotted") + theme_bw() + labs (x = "Year", y = "Annual Park Visitors", title = "Channel Islands NP Visitation", subtitle = "(1963-2016)")

gg_base + geom_line (color = "purple") + geom_point (color = "orange", aes (size = year), alpha = 0.5)
gg_base + geom_col (fill = "orange", color = "purple") + geom_line (colr = "green")

ggplot(data = ca_np, aes(x = year, y = visitors, group = park_name)) + geom_line(aes(color = park_name))




```{r}
gg_np <- ggplot(data = ca_np, aes(x = year, y = visitors, group = park_name))
gg_np +
  geom_line(show.legend = FALSE) +
  theme_light() + 
  labs(x = "year", y = "annual visitors") +
  facet_wrap(~ park_name)
```



ggsave(here("figures", "np_graph.jpg"), dpi = 180, width = 8, height = 7)
